FoRTE baseline

### 2019-01-29 analysis/paper/paper.Rmd
Add some notes to paper.Rmd

Here is a citation [@bond-lamberty_2015_moderate] and another citation [@clm45_note;@norman_1979_modelling].
Another citation [@bond-lamberty_2015_moderate].

>>>>

Net ecosystem productivity (NEP) declines immediately after disturbance, but recovers in 10-20 years [@amiro_2010_ecosystem].
Extent of recovery depends on balance of gross (aboveground?) primary productivity (GPP) and respiration; GPP increase during recovery, while respiration may stay constant [@amiro_2010_ecosystem].
